Detecting Stylistic Variation in Pop Production

### 2023-11-30 outputs/paper/paper.qmd
cut fluff from conclusion

Our analysis reveals that the amalgamation of crowdsourced metrics (like danceability) and machine-listening variables offers a nuanced approximation of musical style. This approach not only mirrors the multifaceted nature of auditory perception, but also enriches our model's capacity to capture the essence of an artist's style. Interestingly, the subjective nature of crowdsourced metrics, which might initially seem rudimentary, plays a crucial role in this process. Our study suggests that they can shape a more intuitive and embodied understanding of music, enhancing the overall analysis. For instance, the work of Martikainen et al. illustrates this point effectively (@podstyle). They combine open-source audio tools with qualitative, crowd-sourced listener data to understand audio-based stylistic variation in podcasts. This synergy between human subjectivity and algorithmic precision underlines the importance of blending these methods for a comprehensive analysis.

However, it's important to note that while these features offer a quantitative lens to examine music, they cannot fully encapsulate the nuanced and subjective aspects of musical style and creativity. The role of human subjectivity is pivotal in interpreting and experiencing music, and this aspect becomes even more significant when considering the broader scope of music recommendation systems. As Nick Seaver's anthropological study of music recommendation companies shows, engineers "develop ways of thinking about musical preference and software, attempting to reconcile them with each other" (@citeSeaver). Engineers' understandings of style and taste influence the designs of the music recommendation systems they build. This extends to a more nuanced understanding of recommendation systems as a whole, highlighting the intricate balance between computational measures and human interpretation in the evolving landscape of music analysis and appreciation.

>>>>

This approach not only mirrors the multifaceted nature of auditory perception, but also enriches our model's capacity to capture the essence of an artist's style. While crowdsourced metrics might initially seem rudimentary, this subjective aspect can play a crucial role in this process. The work of Martikainen et al. illustrates this point effectively, combining open-source audio tools with qualitative, crowd-sourced listener data to understand audio-based stylistic variation in podcasts (@podstyle).

The role of human subjectivity is pivotal in interpreting and experiencing music, and this aspect becomes even more significant when considering the broader scope of music recommendation systems. As Nick Seaver's anthropological study of music recommendation companies shows, engineers "develop ways of thinking about musical preference and software, attempting to reconcile them with each other" (@citeSeaver). Engineers' understandings of style and taste influence the designs of the music recommendation systems they build. Our study therefore contributes to a more nuanced understanding of recommendation systems as a whole, highlighting the intricate balance between computational measures and human interpretation in the evolving landscape of music analysis and appreciation.
